STAT0030_ICA2

### 2019-02-17 STAT0030_ICA2/STAT0030_ICA2.Rmd
PDF create
STAT0030_begin

---
title: "STAT0030_ICA2"
author: "Hongwei Peng"
date: "10/02/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r pressure, echo=FALSE}
plot(pressure)
```

@@

>>>>

---
title: "STAT0030_ICA2"
author: "Hongwei Peng"
date: "10/02/2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

@@

```{r pressure, echo=TRUE}
plot(pressure)
```

@@

```{r table}
library(knitr)
kable(cars)
```

```{r table2}
kable(PlantGrowth, col.names=c("Weight", "Group"), align=c("c","c"), 
      caption = "Table 2. Plant Growth Data")#this is a test
```
